Proposal: Proving Termination of \texttt{zelda-mosaic} Algorithms under Conditions on the Input

### 2021-02-26 proposal/proposal.tex
correct casing

We have previously developed \texttt{zelda-mosaic}~\cite{zelda_mosaic} which
includes MatLab~\cite{matlab} code to create tiled ``mosaics'' from a set of
smaller input images. We propose now to prove termination of our
mosaic-generation algorithms.

@@

Now we propose to examine these algorithms as implemented in the MatLab source
and prove, if possible, their termination given well-conditioned input. What
necessary conditions are remains to be seen, but likely includes constraints on
the sizes of each individual input image and the size of the key-art target
image.

>>>>

We have previously developed \texttt{zelda-mosaic}~\cite{zelda_mosaic} which
includes MATLAB~\cite{matlab} code to create tiled ``mosaics'' from a set of
smaller input images. We propose now to prove termination of our
mosaic-generation algorithms.

@@

Now we propose to examine these algorithms as implemented in the MATLAB source
and prove, if possible, their termination given well-conditioned input. What
necessary conditions are remains to be seen, but likely includes constraints on
the sizes of each individual input image and the size of the key-art target
image.
